%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Sergio}{GarcíaPrado}
\address{La Paz, 7 3ºC, Palencia, Spain}
\mobile{(+34) 696 904 878}
%%% Social
\email{garciparedes@gmail.com}
\homepage{garciparedes.me}
\github{garciparedes}
\linkedin{garciparedes}
%%% Optionals
\position{Junior Computer Scientist}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {.\linebreak\linebreak\linebreak}
\letterdate{\today}
\lettertitle{Internship Application for Computer Science student}
\letteropening{Dear Mr./Ms./Dr./Dra. ,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Sergio García Prado~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}

    \paragraph{}
    I'm interested in the internship with the Development Department during summer quarter. I'm a Junior at the University of Valladolid, Spain, pursuing a bachelor's degree in Computer Science with mention in Computation. These years at university has sparked my interest in more complex part of Computer Science. I believe in the important weight that has these with you and would be excited to be an intern with your organization.

    \paragraph{}
    During the last year of college I discover that really like data analysis, ie, big data, cryptography, optimization methods, advanced algorithms and all related with study, find and coding the better method to solve any kind of problem. I intend to graduate on third quater of 2016 and I'm looking for experience that is applicable to my yield.

    \paragraph{}
    I am confident that my experiences, skills and strong interests in the goals of your company have prepared me to be a strong intern for your program. Maybe my English fluency is limited but I am convinced that I can adapt to a work environment in another language. I have attached my resume and look forward to discussing my qualifications with you. Thank you for your time and consideration.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
