% !TEX encoding = UTF-8 Unicode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[english]{babel}


\usepackage{fontawesome}

\begin{document}

    \header{Sergio}{GarcíaPrado}{junior data \{ engineer, scientist \}} % Your name and current job title/field

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

    \begin{aside} % In the aside, each new line forces a line break

        \section{contact}
            ~
            \href{http://garciparedes.me}{\textbf{garciparedes.me}}
            ~
            \href{tel:+34 696 904 878}{+34 696 904 878}
            \href{mailto:sergio@garciparedes.me}{sergio@garciparedes.me}
        \section{social}
            \href{https://github.com/garciparedes}{\quad{\color{red} $\varheartsuit$}\quad\textbf{Github}\quad\faGithub }
            \href{https://es.linkedin.com/in/garciparedes/en}{LinkedIn\quad\faLinkedin }
            \href{http://stackoverflow.com/users/3921457/garciparedes}{Stack Overflow\quad\faStackOverflow }
            \href{https://medium.com/@garciparedes}{Medium\quad\faMedium }
            \href{https://www.kaggle.com/garciparedes}{Kaggle\quad\faTrophy }
        \section{languages}
            spanish bilingual
            english medium
    \end{aside}



%-------------------------------------------------------------------------------
%	SUMMARY SECTION
%-------------------------------------------------------------------------------

  \section{cover letter}

    \noindent Dear recruiter,

    \paragraph{}
    I'm interested in the internship with the Development Department during summer quarter. I'm a Junior at the University of Valladolid, Spain, pursuing a bachelor's degree in Computer Science with mention in Computation. These years at university has sparked my interest in more complex part of Computer Science. I believe in the important weight that has these with you and would be excited to be an intern with your organization.

    \paragraph{}
    During the last year of college I discover that really like data analysis, ie, big data, cryptography, optimization methods, advanced algorithms and all related with study, find and coding the better method to solve any kind of problem. I intend to graduate on third quater of 2016 and I'm looking for experience that is applicable to my yield.

    \paragraph{}
    I am confident that my experiences, skills and strong interests in the goals of your company have prepared me to be a strong intern for your program. Maybe my English fluency is limited but I am convinced that I can adapt to a work environment in another language. I have attached my resume and look forward to discussing my qualifications with you. Thank you for your time and consideration.


    \noindent Regards,
    \newline Sergio García Prado.

\end{document}
